Prediction of the 2020 Presidential Election

### 2020-11-01 outputs/paper/paper.Rmd
added more references, saving rds locations for individual data and poststrat

library(tidyverse)
library(tinytex)
library(readr)
```

@@

We are running our regression model using the 'glm()' function in [R]. The fitted model results in the following coefficients:
```{r}
```

>>>>

library(tidyverse)
library(tinytex)
library(readr)
library(here)
```

@@

We are running our regression model using the 'glm()' function in [R]. The fitted model results in the following coefficients:
```{r}

#Loading in the final model and the coefficents of the model in this cell. Please note that the outputs of those models are being stored in the outputs/model directory. The here package should give you the same result but if it doesn't then you may have to manually enter the same directory.
final_model <- readRDS(here::here("outputs/model","final_model.rds"))
coefficients <- readRDS(here::here("outputs/model","coefficients.rds"))

cor <- readRDS(here::here("outputs/model","cor.rds"))
